# Statistical Inference Quiz 2
Muralidhar Areti  
Jul 19, 2015

# Introduction

## Q1
What is the variance of the distribution of the average IID draw of n observations from a population with mean mu and variance sigma^2^

Ans: sigma^2^/n

## Q2
Suppose that the diastolic blood pressures (DBPs) for men aged 35-44 are normally distributed with a mean of 80 mm Hg and a standard deviation of 10. What is the probability that a random 35-44 year old has a DBP less than 70?

```{r}
round(pnorm(70, mean=80, sd=10), 2)
```

## Q3
Brain volume for adult women is normally distributed with a mean of about 1,100 cc for women with a standard deviation of 75 cc. What brain volume represents the 95th percentile?

```{r}
round(qnorm(0.95, mean=1100, sd=75), 3)
```

## Q4
Referring to the previous question, brain volume for adult women is about 1,100 cc for women with a standard deviation of 75 cc. Consider the sample mean of 100 random adult women from this population. What is the 95th percentile of the distribution of that sample mean?

```{r}
round(qnorm(0.95, mean=1100, sd=75/sqrt(100)), 3)
```

## Q5
You flip a fair coin 5 times, about what's the probability of getting 4 or 5 heads?
```{r}
choose(5,4)*0.5^5 + choose(5,5)*0.5^5
```

## Q6
The respiratory disturbance index (RDI), a measure of sleep disturbance, for a specific population has a mean of 15 (sleep events per hour) and a standard deviation of 10. They are not normally distributed. Give your best estimate of the probability that a sample mean RDI of 100 people is between 14 and 16 events per hour

```{r}
1 - pnorm(-abs(1))*2
```

## Q7
Consider a standard uniform density. The mean for this density is 0.5 and the variance is 1/12. You sample 1,000 observations from this distribution and take the sample mean, what value would you expect it to be near?

Ans: you would expect it to be very close, if not equal to, the mean

## Q8
The number of people showing up at a bus stop is assumed to be Poisson with a mean of 5 people per hour. You watch the bus stop for 3 hours. About what is the probability of viewing 10 or fewer people?

```{r}
round(ppois(10, lambda=5 * 3), 2)
```

Final Result: 8/8