# Statistical Inference Homework 2
Muralidhar Areti  
Jul 19, 2015

# Introduction

## Q1
The probability that a manuscript gets accepted to a journal is 12%. However, given that a revision is asked for, the probability that it gets accepted is 90%. Is it possible that the probability that a manuscript has a revision asked for is 20%?

Hint:  
* A = Accepted
* B = Revision
* P(A) = 0.12
* P(A|B) = 0.90
* P(B) = 20

Answer:  
P(AnB) = P(A|B) * P(B) = 0.9 x 0.2 = 0.18. This is larger than P(A) = 0.12 which is not possible since A n B c A (A intersects B subsets A). 

## Q2
Suppose that the number of web hits to a particular site are approximately normally distributed with a mean of 100 hits per day and a standard deviation of 10 hits per day. What is the probability that a given day has fewer than 93 hits per day expressed as a percentage to the nearest percentage point?

Hint:   
Let X be the number of hits per day. We want P(X <= 93) given that X is N(100, 10^2^). 

Answer:  
```{r}
round(pnorm(93, mean=100, sd=10) * 100)
```

## Q3
Suppose 5% of housing projects have issues with asbestos. The sensitivity of a test for asbestos is 93% and the specificity is 88%. What is the probability that a housing project has no asbestos given a negative test expressed as a percentage to the nearest percentage point?

Hint:  
* A = asbestos
* T<sub>+</sub> = test positive
* T<sub>-</sub> = test negative
* P(T<sub>+</sub>|A) = 0.93
* P(T<sub>-</sub>|A^c^) = 0.88
* P(A) = 0.05

Answer:  
```{r}
(0.88 * 0.95) / (0.88 * 0.95 + 0.07 * 0.05)
```

## Q4
Suppose that the number of web hits to a particular site are approximately normally distributed with a mean of 100 hits per day and a standard deviation of 10 hits per day. 

### Part 1
What number of web hits per day represents the number so that only 5% of days have mroe hits? Express your answer to 3 decimal places

Hint:  
Let x be the number of hits per day. We want x so that F(x) = 0.95

Answer:  
```{r}
round(qnorm(0.95, mean=100, sd=10), 3)
```

or  
```{r}
round(qnorm(0.95, mean=100, sd=10, lower.tail=FALSE), 3)
```

### Part 2
Imagine taking a random sample fo 50 days. What number of web hits would be the point so that only 5% of averages of 50 days of web traffic have more hits? Express your answer to 3 decimal places

Hint:  
Let X be the average number of hits per day for 50 randomly sampled days. X is N(100, 10^2^/50)

Answer:  
```{r}
round(qnorm(0.95, mean=100, sd=10/sqrt(50)), 3)
```

or
```{r}
round(qnorm(0.95, mean=100, sd=10/sqrt(50), lower.tail=FALSE), 3)
```

## Q5
You don't believe that your friend can discern good wine from cheap. Assuming that you are right, in a blind test where you randomize 6 paired varieties (Merlot, Chianti, ...) of cheap and expensive wines.

What is the chance that she gets 5 or 6 right expressed as a percentage to 1 decimal place?

Hint:  
Let p = 0.5 and X be binomial

Answer:  
```{r}
round(pbinom(4, prob=0.5, size=6, lower.tail=FALSE) * 100, 1)
```

## Q6
Consider a uniform distribution. If we were to sample 100 draws from a uniform distribution (which has a mean of 0.5 and variance of 1/12) and take their mean, Xbar

What is the approximate probability of getting as large as 0.51 or larger expressed to 3 decimal places?

Hint:  
Use the central limit theorem that says Xbar ~ N(mu, sigma^2^/n)

Answer:  
```{r}
round(pnorm(0.51, mean=0.5, sd=sqrt(1/12/100), lower.tail=FALSE), 3)
```

## Q7
If you roll ten standard dice, take their average, then repeat this process over and over and construct a histogram, what would be its variance expressed to 3 decimal places?

Hint:  
Var(Xbar) = sigma^2^/n

Answer:  
The answer will be 0.292 since the variance of the sampling distribution of the mean is sigma^2^/10 where sigma^2^ is the variance of a single die roll which is
```{r}
mean((1:6-3.5)^2 / 10)
```

## Q8
The number of web hits to a site is Poisson with mean 16.5 per day. What is the probability of geting 20 or fewer in 2 days expressed as a percentage to one decimal place?

Hint:  
Let X be the number of hits in 2 days then X ~ Poisson(2Lambda)

Answer:  
```{r}
round(ppois(20, lambda=16.5 * 2) * 100, 1)
```